---
title: "p8105_hw1_sx2337"
author: "Shun Xie"
date: "2022-09-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Problem 1

In the first step, I install and load the penguins dataset.

```{r}
#install.packages("palmerpenguins")
data("penguins", package = "palmerpenguins")
```

Now I can call the dataset and see the summary of the dataset using summary():

```{r}
summary(penguins)
```


There are ```r length(penguins)``` number of variables in the dataset, namely species, island, bill_length measuring in mm, bill_depth measuring in mm, flipper_length measuring in mm, body_mass measuring in g, sex and year. The data is recorded from year 2007 to year 2009. The size of the data is ```r ncol(penguins)``` columns and ```r nrow(penguins)``` rows. So there are a total of ```r nrow(penguins)``` individuals included in the dataset.

In the summary, can see that there are three types of species of penguins, namely Adelie, Chinstrap and Gentoo, living on the three islands: Biscoe, Dream and Torgersen. Bill length, bill depth, flipper length and body mass are all continuous variables. The mean